Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-05-06 longSC.tex
final from Ante's comments

\section{Results}
\label{sec:results}

@@

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
        \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics from $2^{\rm nd}$ up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands. Note that the systematic and statistical errors are combined in quadrature for these lower order harmonic correlations and SC(4,2) and SC(3,2) are scaled by a factor of 0.1. Systematic uncertainties are represented with boxes for higher order harmonic correlations.}
        \label{fig:Figure_1}
              \end{center}
\end{figure*}

@@

%\begin{figure*}
%	\begin{center}
%        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_SC_ptdep}}
%        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4_QConly_nSC_ptdep}}
%	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_SC_ptdep}}
%        	\resizebox{0.42\columnwidth}{!}{\includegraphics{figs/fig4b_QConly_nSC_ptdep}}
%        \caption{SC(3,2) and SC(4,2) with low (a) and high (c) minimum $p_{\rm T}$ cuts, and normalized SC(3,2) and SC(4,2) ((b) and (d)) in $\PbPb$ collisions at $\snn=2.76$~TeV. Panels (a) and (b) show the results for the minimum $p_{\rm T}$ range $0.2<p_{\rm T, min}<0.7$~GeV/$c$ and panels (c) and (d) are for the minimum $p_{\rm T}$ range $0.8<p_{\rm T, min}<1.5$~GeV/$c$. Note that NSC data points from each $p_{\rm T, min}$ in a centrality percentile bin are shifted for visibility.}
%        \label{fig:Figure_2}
%        \end{center}   
%\end{figure*}

@@

\section{Model Comparisons}
\label{sec:theory}
%\subsection{Theoretical models}
%\label{sec:models}
%We have used various models in this article. The {\sc HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum. 
%Secondly, the HIJING model was used to estimate the strength of nonflow correlations (typically few-particle correlations insensitive to the collision geometry). 
%We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}. 
We have compared the centrality dependence of our observables with event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}. The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$. 
This model gives a good description of the charged hadron multiplicity and the low $p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Figs.~11-13 in \cite{Niemi:2015qia}).
Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~15 in \cite{Niemi:2015qia}). 
%\textbf{Need a short description of event-by-event viscous hydrodynamic calculations from VISH2+1}.

@@

%Two mechanisms in {AMPT} produce collective effects: partonic and hadronic rescattering. Before partonic rescattering, the initially produced strings may be broken into smaller pieces by the %so-called string melting. Three different {AMPT} settings are considered, having either string melting or hadronic rescattering or both activated.

\subsection{Centrality Dependence of SC($m$,$n$) and NSC($m$,$n$)}
\label{sec:theory_allorder}

%\begin{figure*}[!]
%	\begin{center}
%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_vish.eps}}
%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_vish.eps}}
%        \caption{SC(3,2) (a) and SC(4,2) (b) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf} with different settings. Upper (lower) panels show SC($m$,$n$) (NSC($m$,$n$)).
%        Calculations with AMPT, MC-KLN, and MC-Glauber initial conditions are drawn as different colors and markers. The $\eta/s$ parameters are shown in different line styles, the small $\eta/s=0.08$ are shown as solid lines, and large $\eta/s$~(0.2 for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines. }
%         \label{fig:Figure_3}
%        \end{center}   
% \end{figure*}
% 
%\begin{figure*}[!]
%	\begin{center}
%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_ampt.eps}}
%        	\resizebox{0.40\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_ampt.eps}}
%        \caption{SC(3,2) (a) and SC(4,2) (b) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
%        \label{fig:Figure_4}
%        \end{center}   
% \end{figure*}

%\subsection{Higher Order Harmonic Correlations}
%\label{sec:theory_highorder}
The SC($m$,$n$) and NSC($m$,$n$) observables are compared to several theoretical calculations. The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}. 
In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is negative in the data in 0--10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
This observation helps us to better understand the fluctuations in initial energy density.
The NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values. This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions in models of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
%, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
The measurement of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions.
%Better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.

%SC($m$,$n$) and NSC($m$,$n$) for $m$+$n$$<$7
While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations best are compared to the results in Fig.~\ref{fig:Figure_3}. 
As can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for ``param1'' parameterization the phase transition from the hadronic to the QGP phase occurs at the lowest temperature, around 150~MeV. This parameterization is also characterized by a moderate slope in $\eta/s(T)$ which decreases (increases) in the hadronic (QGP) phase.
The model calculations in which the temperature of the phase transition is larger than for the ``param1'' can be ruled out by the previous measurements~\cite{ALICE:2016kpq}.
As shown in Fig.~\ref{fig:Figure_3}, only the correlations between $v_5$ and $v_2$ are well described for all available centralities. 
On the other hand, for correlations between $v_5$ and $v_3$ the description fails in more peripheral collisions, providing further independent constraints for the models.
%The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$. 
In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the anticorrelation in the data significantly.
Most notably, this measurement is so far the most dramatic example of the failure of constant $\eta/s$ to describe the data.

%\begin{figure*}[!]
%            \begin{center}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT_backup.eps}}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT_backup.eps}}
%                \end{center}
%        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
%        \label{fig:Figure_5_0}
%\end{figure*}
%

@@

%\begin{figure*}[!]
%            \begin{center}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_EKRT.eps}}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_EKRT.eps}}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_EKRT.eps}}
%              \end{center}
%        \caption{Measurements of  SC(5,2) (a), SC(5,3) (b) and SC(4,3) (c) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}        
%        \label{fig:Figure_5}
%\end{figure*}
The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.  All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of all order SC($m$,$n$) observables shown on the left panels in Fig.~\ref{fig:Figure_4}.
Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured but it cannot describe the data quantitively for most of the centrality ranges.
Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 0--10\% central collisions. The NSC(3,2) observable does not show strong sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
Even though NSC(4,2) favors both AMPT initial conditions with $\eta/s=0.08$ and MC-Glauber initial conditions with $\eta/s=0.20$,
SC(4,2) can only be described by models with smaller $\eta/s$. Hence the calculation with large $\eta/s=0.20$ is ruled out. We conclude that $\eta/s$ should be small and that AMPT initial conditions are favored by the data.
The NSC(5,2) and NSC(5,3) observables are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions. The NSC(4,3) observable shows sensitivity to both initial conditions and $\eta/s$ parameterizations.
% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations.
The SC(4,3) results are clearly favored by smaller $\eta/s$ values but NSC(4,3) cannot be described by these models quantitively.

@@

%\begin{figure*}[!]
%	\begin{center}
%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_vish.eps}}
%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_vish.eps}}
%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_vish.eps}}
%        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
%        \label{fig:Figure_6}
%        \end{center}   
% \end{figure*}

@@

%  \begin{figure*}[!]
%	\begin{center}
%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_ampt.eps}}
%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_ampt.eps}}
%        	\resizebox{0.32\columnwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_ampt.eps}}
%        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models. Upper (lower) panels show SC$(m,n)$ (NSC$(m,n)$).}
%        \label{fig:Figure_7}
%        \end{center}   
% \end{figure*}

@@

%It should be noted that the better agreement for SC$(m,n)$ should not be overemphasized since there are discrepancies in the individual $v_n$ between AMPT and data as it was demonstrated for SC(3,2).
%Hence the simultaneous description of SC$(m,n)$ and NSC$(m,n)$ should give better constrains to the parameters in AMPT.
%Can we conclude that the hadronic rescattering only can reproduce the correlation strength well ?
%Considering the underestimated $NSC(4,3)$ in VISH2+1 calculation can be compensated by hadronic rescattering a.l.a ...... ?

@@

\appendix
\section{Model comparison of the Individual $v_n$}

While the centrality dependence of the SC observables is compared to various models, it is still worthwhile to do quantitative comparison of individual flow harmonics $v_n$ to the various models.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v2.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v3.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v4.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
        \label{fig:Figure_8}
              \end{center}
\end{figure*}
\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v2.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v3.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v4.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
        \label{fig:Figure_9}
              \end{center}
\end{figure*}
\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v2.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v3.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v4.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.}
        \label{fig:Figure_10}
              \end{center}
\end{figure*}

>>>>

\section{Results}
\label{sec:results}
\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
        \caption{The centrality dependence of SC($m$,$n$) (a) and NSC($m$,$n$) (b) with flow harmonics from $2^{\rm nd}$ up to $5^{\mathrm{th}}$ order in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from \cite{ALICE:2016kpq} and shown as bands. Note that the systematic and statistical errors are combined in quadrature for these lower order harmonic correlations and SC(4,2) and SC(3,2) are scaled by a factor of 0.1. Systematic uncertainties are represented with boxes for higher order harmonic correlations.}
        \label{fig:Figure_1}
              \end{center}
\end{figure*}

@@

@@

@@

\section{Model Comparisons}
\label{sec:theory}
We have compared the centrality dependence of our observables with event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}. The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$. 
This model gives a good description of the charged hadron multiplicity and the low $p_{\rm T}$ region of the charged hadron spectra at RHIC and the LHC (see Figs.~11-13 in \cite{Niemi:2015qia}).
Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions (see Fig.~15 in \cite{Niemi:2015qia}).

@@

\subsection{Centrality Dependence of SC($m$,$n$) and NSC($m$,$n$)}
\label{sec:theory_allorder}
The SC($m$,$n$) and NSC($m$,$n$) observables are compared to several theoretical calculations. The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}. 
In this previous work it was demonstrated that NSC(3,2) is sensitive mainly to the initial conditions, while NSC(4,2) is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is negative in the data in 0--10\% central collisions while it is positive in the models where the anisotropies originate mainly from fluctuations.
This observation helps us to better understand the fluctuations in initial energy density.
The NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe either the centrality dependence or the absolute values. This observed discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions in models of heavy-ion collisions needs to be revisited to further constrain $\eta/s(T)$.
%, considering the difficulties in separating the role of $\eta/s$ from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
The measurement of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints for the detailed modeling of fluctuating initial conditions.
%Better constraints on the initial state conditions will certainly reduce the uncertainties in determining $\eta/s(T)$.

@@

While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations best are compared to the results in Fig.~\ref{fig:Figure_3}. 
As can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for ``param1'' parameterization the phase transition from the hadronic to the QGP phase occurs at the lowest temperature, around 150~MeV. This parameterization is also characterized by a moderate slope in $\eta/s(T)$ which decreases (increases) in the hadronic (QGP) phase.
The model calculations in which the temperature of the phase transition is larger than for the ``param1'' can be ruled out by the previous measurements~\cite{ALICE:2016kpq}.
As shown in Fig.~\ref{fig:Figure_3}, only the correlations between $v_5$ and $v_2$ are well described for all available centralities. 
On the other hand, for correlations between $v_5$ and $v_3$ the description fails in more peripheral collisions, providing further independent constraints for the models.
%The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$. 
In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the anticorrelation in the data significantly.
Most notably, this measurement is so far the most dramatic example of the failure of constant $\eta/s$ to describe the data.

@@

The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.  All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of all order SC($m$,$n$) observables shown on the left panels in Fig.~\ref{fig:Figure_4}.
Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured but it cannot describe the data quantitively for most of the centrality ranges.
Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 0--10\% central collisions. The NSC(3,2) observable does not show strong sensitivity to the initial conditions nor to the different $\eta/s$ parameterizations used in the models and cannot be described quantitatively by these models.
However, NSC(4,2) is sensitive both to the initial conditions and the $\eta/s$ parameterizations used in the models.
Even though NSC(4,2) favors both AMPT initial conditions with $\eta/s=0.08$ and MC-Glauber initial conditions with $\eta/s=0.20$,
SC(4,2) can only be described by models with smaller $\eta/s$. Hence the calculation with large $\eta/s=0.20$ is ruled out. We conclude that $\eta/s$ should be small and that AMPT initial conditions are favored by the data.
The NSC(5,2) and NSC(5,3) observables are quite sensitive to both the initial conditions and the $\eta/s$ parameterizations.
Similar to the hydrodynamic calculations mentioned above~\cite{Niemi:2015qia}, the sign of NSC(4,3) in these models is opposite to its sign in the data in 0--10\% central collisions. The NSC(4,3) observable shows sensitivity to both initial conditions and $\eta/s$ parameterizations.
% while NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations.
The SC(4,3) results are clearly favored by smaller $\eta/s$ values but NSC(4,3) cannot be described by these models quantitively.

@@

@@

@@

%\input{appendix.tex}
